Tools for Identifying Partisan Gerrymandering (PA)

### 2019-06-05 Latex/Figures/_density_2016.tex
draft revisions

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Compactness Example: District 6 of the Court Adopted Remedial Plan and District 7 of the 2011 Plan
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Compactness Example: District 6 of the Court Adopted Remedial Plan and District 7 of the 2011 Plan}
    \label{fig:compact}
    \includegraphics[width=1\textwidth]{Figures/fig_compactness.pdf}
    \end{center}
    \tabnotes{District 7 of the Enacted plan is recognized as the ``Goofy kicking Donald Duck'', while District 6 of the Remedial map has the same geographic center.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================

>>>>

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Simulated 2016 Elections by Plan
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Simulated 2016 Elections by Plan}
    \label{fig:density2016}
    \includegraphics[width=1\textwidth]{Figures/fig_sims_2016_maps_density.pdf}
    \end{center}
    \tabnotes{Plots based on the 2016 Five Election Composite data centered at the 2016 vote share. All percentages in terms of Republican share of the two-party vote from the composite measure of five state-wide races in 2016. Shaded area contains one standard deviation on either side of the mean, representing 68\% of the simulated seat percentages.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================

### 2019-06-05 Latex/Figures/_density_2018.tex
draft revisions

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Simulated 2016 Elections by Plan
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Simulated 2016 Elections by Plan}
    \label{fig:density2016}
    \includegraphics[width=1\textwidth]{Figures/fig_sims_2016_maps_density.pdf}
    \end{center}
    \tabnotes{Plots based on the 2016 Five Election Composite data centered at the 2016 vote share. All percentages in terms of Republican share of the two-party vote from the composite measure of five state-wide races in 2016. Shaded area contains one standard deviation on either side of the mean, representing 68\% of the simulated seat percentages.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================

>>>>

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Simulated 2018 Elections by Plan
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Simulated 2018 Elections by Plan}
    \label{fig:density2018}
    \includegraphics[width=1\textwidth]{Figures/fig_sims_2018_maps_density.pdf}
    \end{center}
    \tabnotes{Plots based on the 2016 Five Election Composite data centered at the 2018 vote share. All percentages in terms of Republican share of the two-party vote from the composite measure of five state-wide races in 2016. Shaded area contains one standard deviation on either side of the mean, representing 68\% of the simulated seat percentages.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================

### 2019-06-05 Latex/Figures/_density_congress.tex
draft revisions

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Simulated 2018 Elections by Plan
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Simulated 2018 Elections by Plan}
    \label{fig:density2018}
    \includegraphics[width=1\textwidth]{Figures/fig_sims_2018_maps_density.pdf}
    \end{center}
    \tabnotes{Plots based on the 2016 Five Election Composite data centered at the 2018 vote share. All percentages in terms of Republican share of the two-party vote from the composite measure of five state-wide races in 2016. Shaded area contains one standard deviation on either side of the mean, representing 68\% of the simulated seat percentages.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================

>>>>

% # •••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••••
% Comparing the Simulated Elections with US Congressional Elections (PA)
% =================================================================
% -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE -- FIGURE --   % 
% ----------------------------------------------------------------- 
\begin{figure}
    \begin{center}
    \caption{Comparing the Simulated Elections with US Congressional Elections (PA)}
    \label{fig:densityplots_congressional}
    \includegraphics[width=1\textwidth]{Figures/fig_sims_actual_density.pdf}
    \end{center}
    \tabnotes{Plots based on the 2016 Five Election Composite data centered at the vote share for each year. All percentages in terms of Republican share of the two-party vote from the composite measure of five state-wide races in 2016. Shaded area contains one standard deviation on either side of the mean, representing 68\% of the simulated seat percentages.}
\end{figure}
% -----------------------------------------------------------------
% -- END FIGURE -- END FIGURE -- END FIGURE -- END FIGURE -- END FI %
% =================================================================
